\begin{abstract}
This paper began with a simple question: what happens when Hebrew divine names are examined not only through gematria, but also through base conversion, digit sums, and numerical symmetry? The answer was not one perfect system in which every name behaves alike. What emerged was more interesting: overlapping patterns, with certain names and formulas sitting at unusually dense intersections.

The clearest examples include YHWH, $26_{10}=22_{12}$; Shaddai, $314_{10}=222_{12}$; Ehyeh Asher Ehyeh, $543_{10}=393_{12}$; Elohim, $86_{10}=72_{12}$; and El Olam, whose Mispar Gadol value is $737_{10}=515_{12}$. The shorter repeated-digit results belong to the exact ladder $dd_{12}=13d$. Its declared source-secure nodes, including exact components and formulas, occupy the rungs $\{1,2,3,4,5,7\}$. Among all six-rung selections from the eleven possibilities, only one other arrangement contains as many internal additions; the unoccupied $66_{12}$ rung remains explicit. Within a declared Christian layer, Yeshua gives $386_{10}=282_{12}$, placing 8 inside a palindromic $2\ldots2$ frame whose digits sum to 12. A separately audited Psalm 22 case adds another intersection. The superscription phrase \textit{Ayelet HaShachar} gives $954_{10}=676_{12}$; the displayed string 676 equals $26^2$ when read in decimal, while the opening lament contains the consonantal sequence of Yeshua inside the ordinary Hebrew form translated ``from my salvation.'' Yeshua HaMashiach gives $749_{10}=525_{12}$, placing 2 inside the $55_{12}$ value of Adonai while again summing to 12. Among all 132 three-digit base-12 palindromes with a repeated outer digit, these are the only two whose center equals the conventional decimal digital root of the full value and whose digits sum to 12. At the canonical level, the chapter total 929 converts to $655_{12}$, whose unique one-digit palindromic closure is $6556_{12}$. Its outer digits sum to 12, its full notation sums to 22 and then 4, and its converted decimal value sums separately to 12. Among all 132 eligible one-digit closures of three-digit base-12 numerals, it is the only one that combines the notation sum of 22 with the converted-value sum of 12.

I present these findings without asking the numbers to decide their own meaning. A source audit corrects several inherited spellings and separates biblical names, later titles, Christian readings, and traditional formula labels. A matched-control study finds that the primary base-12 palindrome concentration is elevated but not statistically decisive, while the Christian-inclusive results form a stronger exploratory pattern for future testing. The calculations can be checked; the larger questions of selection, intention, and theological significance remain open to the reader.
\end{abstract}
