\section{Expansion Registry and Supplemental Findings}

The inherited 43-row derivation chapter is preserved as the audit record from which the source-controlled corpus was reconstructed. A separate expansion registry then tested 82 additional names, titles, formulas, and translation forms. This separation prevents later discoveries from being inserted silently into the repository-locked 24-row primary analysis set. Every candidate, including every non-hit, remains in the source-controlled registry.

\begin{center}
\small
\begin{tabular}{lrrl}
\toprule
Declared layer & Candidates & Base-12 hits & Evidential status \\
\midrule
Biblical expansion & 56 & 9 & exploratory \\
Christian-comparative expansion & 18 & 8 & exploratory \\
Later-traditional expansion & 8 & 3 & exploratory \\
\bottomrule
\end{tabular}
\end{center}

The counts above include positive and negative results under one fixed arithmetic screen. They are discovery-layer counts, not additions to the locked primary baseline.

\subsection{Restored Result: Yeshua HaMashiach}

The conventional Hebrew Christian title \textit{Yeshua HaMashiach}, \hebrew{ישוע המשיח}, appears in Biblica's modern Hebrew New Testament at Matthew 1:1.\cite{biblica_matthew} The underlying New Testament source is Greek, so this row belongs to the Christian-comparative translation layer rather than the biblical Hebrew layer. The result is restored here as a prior author observation that was absent from the surviving Word document and initial LaTeX transfer.

Using the displayed consonantal form:

\begin{align*}
\text{Yeshua} &= \text{\hebrew{ישוע}}=10+300+6+70=386,\\
\text{HaMashiach} &= \text{\hebrew{המשיח}}=5+40+300+10+8=363,\\
\text{Yeshua HaMashiach} &= 386+363=749_{10}=525_{12}.
\end{align*}

No final letter occurs, so standard gematria and Mispar Gadol are identical. Three exact features follow:

\begin{align*}
7+4+9 &= 20 \rightarrow 2,\\
5+2+5 &= 12,\\
\operatorname{reverse}(525) &= 525.
\end{align*}

The full title is therefore a base-12 palindrome whose displayed duodecimal digits have the exact first-step sum $5+2+5=12$. Its decimal truncated sum ends at 2 rather than 8 or 12.

The later named-frame audit adds two exact descriptions. The center 2 is the conventional decimal digital root of 749, and the outer digits reproduce Adonai at $65_{10}=55_{12}$. In the complete 132-member repeated-frame enumeration, $525_{12}$ and Yeshua's $282_{12}$ are the only forms satisfying both the self-center and digit-sum-12 conditions. The conditions were identified after these values were known, so this is an exhaustive descriptive result rather than a prospective probability.

The definite article is mathematically decisive. The article-free phrase gives

\[
\text{\hebrew{ישוע משיח}}=386+358=744_{10}=520_{12},
\]

which is not palindromic. Adding the attested article \hebrew{ה}, with value 5, changes $520_{12}$ to $525_{12}$. This is an article-mediated symmetry, but not an article chosen only to produce a result: the registered form follows conventional Hebrew translation usage. The contrast is retained as a built-in spelling control.

\subsection{Biblical Expansion Positives}

Nine of the 56 additional biblical candidates produce a base-12 palindrome in standard gematria or Mispar Gadol. The table states the exact value layer and preserves two important object-class qualifications.

\begin{center}
\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.6cm}>{\raggedright\arraybackslash}p{2.7cm}>{\raggedright\arraybackslash}p{2.2cm}>{\raggedright\arraybackslash}p{5.0cm}}
\toprule
Form & Value layer & Base 12 & Admission note \\
\midrule
\endfirsthead
\toprule
Form & Value layer & Base 12 & Admission note \\
\midrule
\endhead
Adonai YHWH & standard and MG, 91 & $77_{12}$ & Exact divine address, Genesis 15:2 \\
YHWH Echad & standard and MG, 39 & $33_{12}$ & Shema identity formula, Deuteronomy 6:4 \\
El Elyon Qoneh Shamayim VaAretz & standard, 1039 & $727_{12}$ & Full attested epithet, Genesis 14:19 \\
Qadosh & standard and MG, 410 & $2\mathrm{A}2_{12}$ & Divine speaker designation, Isaiah 40:25 \\
Kedosh Yaakov & standard and MG, 592 & $414_{12}$ & Attested title, Isaiah 29:23 \\
Eben Yisrael & MG, 1244 & $878_{12}$ & Exact words; syntactic and epithet status require review \\
Shomer Yisrael & standard and MG, 1087 & $767_{12}$ & Attested title, Psalm 121:4 \\
Melekh Yisrael & MG, 1111 & $787_{12}$ & Attested title, Isaiah 44:6 \\
YHWH Tzevaot Hu Melekh HaKavod & standard, 664 & $474_{12}$ & Full identity formula, Psalm 24:10 \\
\bottomrule
\end{longtable}
\end{center}

Compact names, compounds, epithets, and complete formulas are deliberately identified rather than merged. The full Genesis 14:19 and Psalm 24:10 expressions show the same phrase-level principle seen in Ehyeh Asher Ehyeh: a complete formula may carry symmetry absent from a shorter component.

\subsection{Christian and Later Sensitivity Findings}

The Christian-comparative expansion includes eight positive rows. Malakh YHWH gives $117_{10}=99_{12}$, but its admission as a divine designation depends on a stated Christian divine-agent reading. Or HaOlam gives Mispar Gadol $918_{10}=646_{12}$. Several translated titles are positive only in a particular historical orthography: defective \textit{Adoneinu Yeshua HaMashiach} gives $870_{10}=606_{12}$; defective \textit{Ben HaElohim} gives $143_{10}=\mathrm{BB}_{12}$ and Mispar Gadol $1353_{10}=949_{12}$; defective \textit{Davar HaElohim} gives Mispar Gadol $857_{10}=5\mathrm{B}5_{12}$; and defective \textit{HaRoeh HaTov} gives $302_{10}=212_{12}$. Their corresponding plene or modern spellings do not preserve those palindromes.

The bare lexical form \textit{Amen} gives $91_{10}=77_{12}$, but the exact translated title in Revelation 3:14 is \textit{HaAmen}, which is not a palindrome under the same test. It is therefore retained as lexical extraction rather than treated as an exact title hit. These losses are part of the result, not editorial debris.

The later-traditional positives are Melekh HaOlam, $241_{10}=181_{12}$; Avinu Shebashamayim, $761_{10}=535_{12}$; and Qudsha Berikh Hu, whose Mispar Gadol value is $1135_{10}=7\mathrm{A}7_{12}$. The last equals the already recorded Mispar Gadol value of HaKadosh Baruch Hu and is not an independent numerical value.

\subsection{Evidential Status}

The expansion scan broadens the descriptive pattern and exposes fruitful cross-name and formula-level relationships. It also exposes orthographic sensitivity, nested expressions, repeated values, and theological admission choices. For that reason, none of the 82 candidates is retroactively promoted into the frozen primary analysis. Their appropriate role is exploratory evidence and a source for prospectively assembled follow-up corpora.
