\section{Technical Layer Taxonomy}

The taxonomy is layered rather than single-cluster. A name may carry a collapse endpoint, a palindrome, a canonical signature, and a thematic interpretation at once. These layers are related, but they are not interchangeable.

The source registry is the authority for form and corpus membership. The counts below are recalculated from the 24-row primary biblical layer; later rabbinic or liturgical forms and messianic-comparative entries are reported separately.

\subsection{Source-Controlled Baseline}

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{3.4cm}r>{\raggedright\arraybackslash}p{9.0cm}}
\toprule
Layer & Primary rows & Meaning \\
\midrule
Strict 8 layer & 10 & a stated decimal or base-12 notation path ends at 8 \\
Exact first-step 12-sum & 8 & a stated decimal or base-12 digit sum equals 12 immediately \\
Base-10 palindrome & 5 & decimal symmetry in standard or Mispar Gadol \\
Base-12 palindrome & 5 & duodecimal symmetry in standard or Mispar Gadol \\
\bottomrule
\end{tabular}
\end{center}

The categories overlap. They describe properties of the admitted strings, not mutually exclusive theological classes.

\subsection{Layer 1: Strict 8}

A strict 8 layer is assigned when the standard total, Mispar Gadol total, or either base-12 notation-collapse reaches 8 under the stated stopping rule. The ten primary rows are:

\begin{itemize}
\item YHWH;
\item Shaddai;
\item El Elyon;
\item El Olam;
\item El Roi;
\item El Gibbor;
\item El Yeshuati;
\item source-form Elohei HaAretz;
\item source-form Elohei Avraham;
\item source-form Elohei Yaakov.
\end{itemize}

Agency, action, power, or judgment may be proposed as interpretations of this layer, but those themes do not create the endpoint.

\subsection{Layer 2: Exact First-Step 12-Sums}

The eight primary rows with an exact first-step sum of 12 are:

\begin{itemize}
\item Ehyeh Asher Ehyeh;
\item El Olam;
\item source-form Elohei HaShamayim;
\item source-form Elohei HaAretz;
\item El Shaddai;
\item source-form HaEl HaGadol;
\item source-form Elohei Yitzchak;
\item source-form Elohei Yaakov.
\end{itemize}

The source corrections matter. HaEl HaGadol is $84_{10}$ and therefore gives the immediate equality $8+4=12$; the inherited form without the first article was $79_{10}$. Shekhinah remains outside the exact 12-sum layer under its attested later form, and classical Ribbono Shel Olam is $740_{10}$ rather than the inherited 750.

\subsection{Layer 3: Base-10 Palindromes}

The five primary rows with a base-10 palindrome in either standard gematria or Mispar Gadol are:

\begin{itemize}
\item Elohim = 646 under Mispar Gadol;
\item El Olam = 737 under Mispar Gadol;
\item El Roi = 242;
\item El Gibbor = 242;
\item source-form Elohei HaShamayim = 1001 under Mispar Gadol.
\end{itemize}

The shared value 242 between El Roi and El Gibbor remains a strong exact cross-link. HaMakom = 191 and HaRachaman = 303 add palindromes only in the declared later-traditional sensitivity layer.

\subsection{Layer 4: Base-12 Palindromes}

The five primary rows with a base-12 palindrome are:

\begin{itemize}
\item YHWH = 22\textsubscript{12};
\item Adonai = 55\textsubscript{12};
\item Shaddai = 222\textsubscript{12};
\item Ehyeh Asher Ehyeh = 393\textsubscript{12};
\item El Olam = 515\textsubscript{12} under Mispar Gadol.
\end{itemize}

HaKadosh Baruch Hu = 7A7\textsubscript{12} under Mispar Gadol belongs to the later-traditional layer. Yeshua = 282\textsubscript{12} belongs to the inherited messianic-comparative layer, while the restored full title Yeshua HaMashiach = 525\textsubscript{12} belongs to the Christian expansion layer. BEN = 44\textsubscript{12} is a property of a Kabbalistic expansion abbreviation and is not counted as a literal-name discovery.

Across bases 2 through 20, base 12 ranks third for standard-value palindrome count and second for Mispar Gadol count in the primary corpus. Base 3 ranks first under both systems. In the restored 29-row Christian-inclusive layer containing Yeshua HaMashiach, base 12 is tied for first under standard gematria and is the sole leader under Mispar Gadol. These are conditional rankings of declared slices, not competing judgments about whether Yeshua is divine; the separate textual categories make the Christian admission premise explicit. Matched controls show that the primary base-12 elevation does not clear the prespecified correction, while the stronger Christian-inclusive result remains exploratory.

\subsection{Layer 5: Canonical and Structural Signatures}

The main exact contacts are:

\begin{itemize}
\item YHWH gives the base-12 identity string 22\textsubscript{12};
\item Eloah gives decimal 42;
\item Elohim gives $86_{10}=72_{12}$;
\item Shaddai gives 314, an exploratory decimal rendering of $3.14$;
\item El Shaddai gives 345, an exploratory 3-4-5 digit structure;
\item HaKadosh Baruch Hu gives 655 in the later-traditional layer;
\item the scroll construction gives 6556\textsubscript{12} as a separate constructed palindrome.
\end{itemize}

The 42-letter and 72-name traditions are formula-level objects. The four labels AB, SAG, MAH, and BEN state conventional expansion values and are not independent exact-value hits.

The later frame audit adds a second structural layer. Yeshua's $282_{12}$ carries the complete $22_{12}$ value of YHWH as its outer frame, while Yeshua HaMashiach's $525_{12}$ carries the complete $55_{12}$ value of Adonai. Across all 132 three-digit repeated-frame palindromes, these are the only two whose center is the decimal digital root of the full value and whose digits sum to 12. This is an exhaustive finite result discovered after the two examples were known, not a prospective probability.

\subsection{Textual and Interpretive Layers}

The source model preserves several kinds of material without merging them:

\begin{itemize}
\item primary biblical names and titles supply repository-locked primary counts;
\item Shekhinah, HaMakom, HaRachaman, HaKadosh Baruch Hu, and Ribbono Shel Olam form a later-traditional layer;
\item Yeshua, Immanuel, Mashiach, and Sar Shalom form the inherited messianic-comparative layer;
\item Yeshua HaMashiach and the complete Christian candidate registry form a separately declared expansion layer;
\item foreign-deity, constructed, and false prepositional matches are excluded;
\item Kabbalistic formulas and expansion labels are evaluated as special objects.
\end{itemize}

This division is textual rather than theological: it identifies what kind of source establishes each string before asking what that string may mean.

\subsection{Bridge Results}

\paragraph{Yeshua.}
Yeshua remains one of the densest numerical results: $386_{10}=282_{12}$ gives a decimal terminal value of 8 under the declared rule, a decimal digital root matching its center 8, the exact base-12 digit sum $2+8+2=12$, base-12 palindrome structure, and the $22_{12}$ YHWH frame. Its placement in the messianic-comparative layer makes the theological premise explicit without changing the arithmetic.

\paragraph{Yeshua HaMashiach.}
The restored full title gives $749_{10}=525_{12}$. It is palindromic, its center 2 is the decimal digital root of 749, its base-12 digits sum to 12, and its outer frame is Adonai's $55_{12}$. The article-free phrase gives $744_{10}=520_{12}$, so the article's value of 5 creates the exact $525_{12}$ symmetry. This is both a strong full-title result and a transparent demonstration that articles and orthography must remain source-controlled.

\paragraph{Shaddai and El Shaddai.}
Shaddai gives $314_{10}=222_{12}$ and a terminal 8 layer, while El Shaddai gives $345$ and the exact first-step sum $3+4+5=12$. Both source forms are biblical, so this prefix shift remains a clean internal comparison.

\paragraph{El Olam.}
El Olam remains a primary multi-layer bridge through standard 177, Mispar Gadol 737, $515_{12}$, and strict 8/12 contacts. The former shared-value claim with El HaNe'eman does not survive source correction: the attested form includes an initial article and equals 182, not 177.

\paragraph{El Roi and El Gibbor.}
Both forms equal 242, producing an exact shared value, a base-10 palindrome, and collapse to 8. This remains stronger evidence than an association produced only by thematic coding.

\subsection{Summary}

The revised taxonomy separates strict arithmetic, textual layer, and interpretation. It preserves the strongest base-12 and bridge results while exposing which earlier patterns depended on spelling, object-class mixing, or false lexical matches. The structurally matched Hebrew comparison, collapse sensitivity, network stress tests, and complete repeated-frame enumeration are now documented. Further validation should use prospectively frozen divine-title corpora, semantic controls, and lexical-family-aware comparisons rather than unrestricted pattern collection.
