\section{Testing the Pattern Without Explaining It Away}

Once a pattern has been noticed, two opposite mistakes become tempting. One is to protect it from every comparison. The other is to imagine that a comparison can decide whether the pattern is meaningful. I wanted to avoid both. The controls in this study ask how often similar numerical features arise elsewhere; they do not pretend to measure God, intention, or theological truth.

\subsection{What Changed When Other Bases Were Checked}

The 24-row primary biblical corpus was tested in every base from 2 through 20. Under standard gematria, base 12 contains four palindromes and ranks third. Under Mispar Gadol, it contains five and ranks second. Base 3 ranks first under both systems with six palindromes.

This does not mean that base 12 now has fewer palindromes than it had before. YHWH remains $22_{12}$, Adonai remains $55_{12}$, Shaddai remains $222_{12}$, Ehyeh Asher Ehyeh remains $393_{12}$, and El Olam remains $515_{12}$ under Mispar Gadol. The ranking changes only when a different question is asked: \emph{which base produces the largest raw count in this particular frozen corpus?}

Nor does the base-3 result automatically make base 3 the theological center of the paper. A raw count treats every palindrome as one hit. It does not measure whether the hit belongs to YHWH, whether it forms a visible 22 or 72, whether its digits sum to 12, or whether it connects with a canonical construction. Base 3 wins the frequency comparison. Base 12 remains distinctive in the content and intersections of its results. Both statements can be true.

\subsection{What Happened Against Matched Hebrew Phrases}

The primary names were compared with 100,000 simulated sets drawn from 470,793 structurally matched Hebrew Bible phrase types. The controls matched the broad shapes of the names: word count, ordered word lengths, and final-letter count. The question was whether ordinary phrases of similar form often produce as many base-12 palindromes.

\begin{center}
\small
\begin{tabular}{lrrr}
\toprule
Primary value system & Observed & Control mean & Corrected $p$ \\
\midrule
Standard gematria & 4 & 2.001 & 0.135059 \\
Mispar Gadol & 5 & 1.998 & 0.090579 \\
\bottomrule
\end{tabular}
\end{center}

The primary corpus has roughly twice the matched mean under both value systems, but neither result crosses the prespecified corrected 0.05 threshold. The concentration is elevated, but the names and operations predate the experiment, and this control does not establish statistical exceptionality.

\subsection{Why the Christian Layer Remains Interesting}

When Yeshua HaMashiach is restored and the declared Christian titles are included, base 12 ranks first under both value systems. The 29-row Christian-inclusive layer gives corrected probabilities of 0.030240 and 0.016940. The larger 46-row Christian expansion is stronger still.

Those results are promising, but they were assembled after the central patterns were already known and include related expressions. They are therefore exploratory rather than retroactive proof. What they provide is a clear next test: assemble a new Christian title corpus under fixed linguistic rules, freeze it before calculation, and then ask whether the base-12 concentration appears again.

The separation identifies which textual tradition is being tested; it does not decide Yeshua's theological status. Within the Christian layer, the convergence of $282_{12}$, $525_{12}$, the exact sums of 12, and the visible YHWH frame remains one of the paper's strongest patterns.

\subsection{What the Psalm 22 Boundary Shows}

Psalm 22 was selected for its established Passion setting before the numerical result in its superscription was known. Because the particular conjunction in \textit{Ayelet HaShachar} was recognized after inspection, I treat the scan as a bounded exploratory control rather than a prospective probability.

Among the 964 contiguous two-word windows in the first Masoretic verse of the 150 Psalms, 70 are base-12 palindromes under standard gematria and 75 under Mispar Gadol. Exactly one window under either system is both palindromic and composed only of displayed digits that form a decimal perfect square: \hebrew{אילת השחר}, with $954_{10}=676_{12}$ and $676_{10}=26^2$. Within the narrower $4+4$, no-final-form stratum, seven of 79 windows are palindromic; the Psalm 22 phrase is the only one at value 954.

The condition is not unique across arbitrary biblical phrases. Among 282,294 contiguous two-word Tanakh windows, it appears 571 times under standard gematria and 502 under Mispar Gadol. Seven $4+4$, no-final-form windows equal 954; the exact phrase \hebrew{אילת השחר} occurs once.

Negative checks keep the finding localized. Neither individual word, the complete superscription, the quoted cry, the opening verse, the full Psalm, nor \hebrew{מישועתי} is palindromic in base 12. These failures prevent the title phrase from becoming a claim about every numerical level of Psalm 22. Appendix E gives the exact variants, source boundary, and occurrence counts; the repository preserves every generated row.

\subsection{What the Repdigit Ladder Actually Establishes}

The two-digit repeated base-12 numerals form a complete finite family of eleven values:

\[
dd_{12}=13d,
\qquad
d\in\{1,2,\ldots,\mathrm{B}\}.
\]

The source-secure biblical nodes occupy the six rungs $\{1,2,3,4,5,7\}$. Counting relations with two distinct occupied addends, this set contains six closures of the form $a+b=c$. That is the maximum possible for any six-rung subset of the eleven-rung ladder. Exhaustive enumeration of all

\[
\binom{11}{6}=462
\]

subsets finds only two with six such relations:

\[
\{1,2,3,4,5,6\}
\qquad\text{and}\qquad
\{1,2,3,4,5,7\}.
\]

The second is the observed set. The descriptive proportion is therefore $2/462=0.004329$. This is a finite census of rung arrangements, not a prospective probability that six independently selected divine names would land there. The set was recognized after the palindromes were known, and its members mix complete names, nested formulas, and exact components.

Opening the more permissive layers makes the result less selective. Adding rungs 9 and 11 produces ten distinct-addend relations, but 31 of the 165 possible eight-rung subsets have at least that many. The source and spelling qualifications attached to those two added occupants are therefore not hidden behind the stronger core result.

The apparent $66_{12}$ gap was also checked directly. Neither the corrected manuscript registry nor the 82-row expansion registry has an admitted row at decimal value 78 under standard gematria or Mispar Gadol. The Psalm-opening dataset does contain one contiguous two-word window at that value: \hebrew{יהוה בכל} in Psalm 111:1 gives $78_{10}=66_{12}$ under both systems. In context, however, it is the incomplete sequence ``YHWH, with all'' from ``I will thank YHWH with all my heart,'' not a divine title or complete formula.\cite{oshb} Treating it as an occupant would exchange a linguistic boundary for a desired number. I retain it as a negative check and leave rung 6 empty.

\subsection{What the Complete Frame Enumeration Established}

The frame audit asked whether the outer digits of an odd-length base-12 palindrome reproduce the complete base-12 value of another admitted expression. Across the 40 analyzable manuscript objects and all 82 expansion candidates, 30 value layers are eligible odd-length palindromes. Twenty-three of those layers have a named outer frame under the same value system. The five frame values are $22_{12}$ for YHWH, $33_{12}$ for YHWH Echad, $44_{12}$ for BEN, $55_{12}$ for Adonai, and $77_{12}$ for Adonai YHWH. The lexical form Amen also has $77_{12}$ under standard gematria.

That result supplies an important restraint: a named outer frame is not unique to Yeshua, especially after the expansion registry is opened. The narrower repeated-frame result is different. Among every one of the 132 possible palindromes $ada_{12}$, only $282_{12}$ and $525_{12}$ have both a center equal to the conventional decimal digital root and digits summing to 12. Both are stable under standard gematria and Mispar Gadol. They are occupied by Yeshua and Yeshua HaMashiach, and their frames are YHWH and Adonai.

The joint conditions were chosen after those two values were known. The exhaustive count is therefore not a prospective chance probability. It establishes exactly how many solutions exist inside the declared finite family. Appendix D summarizes the audit and its algebra; the repository preserves the complete enumeration, all non-hits, source layers, and frame-family differences.

\subsection{What Happened When the Network Was Stressed}

A separate frozen test treated six selected names as a network around the reference values 8, 12, 22, 42, and 72. The original network contains eight name-to-anchor contacts and three cross-name links. Against 100,000 matched simulations, both scores were elevated after correction. The more revealing result came when one name at a time was removed.

Without Yeshua, five anchor contacts remain, with an adjusted upper-tail probability of 0.011200. Only one cross-name link remains, with an adjusted probability of 0.087609. The broad contact with the anchors therefore does not disappear, but most of the measured connectivity runs through Yeshua. In statistical terms, the link result depends on that central node. In Christian terms, a network whose connections converge on Yeshua may be more coherent, not less. The arithmetic establishes the centrality; the reader must decide whether that centrality is incidental, literary, theological, or some combination of these.

The same distinction applies to exact value collisions. Twenty structurally matched forms also had Yeshua's value 386. Exactly twelve use the same four consonants as Yeshua in another order, leaving eight forms outside that consonant family. Those eight resolve into four different consonant families represented by two forms each:

\[
20=12+8,
\qquad
8=4\times2.
\]

This prevents me from calling 386 lexically unique, but it also gives the control outcome a structure of its own. The twelve are other forms because Yeshua itself was excluded from the control pool; adding the target back would make thirteen attested forms in that consonant family. The 12--8--4 partition was noticed after the results were known, so no prospective probability belongs to it. It remains exact, and its recurrence of the paper's central values is worth placing before the reader. Four of the twelve same-letter forms also have explicit salvation or help language in context, although their numerical equality is mechanically explained by the shared consonants.

\subsection{What the Alternative Anchors Tested}

The fixed routes exposed enough other values to form 840 alternative five-anchor sets with the same one-digit and two-digit shape as the theological set. Of these, 196, or 23.33 percent, equaled or exceeded the set $\{8,12,22,42,72\}$ on both network scores. Some alternatives scored higher. As a numerical selection, then, this particular set is not statistically privileged among the values already available for inspection.

That is an important correction for selection freedom, but it is not a test of whether the alternatives carry the same meanings. The placebo sets treat all attainable numbers as interchangeable. They do not ask whether a value has an independent canonical history, whether it belongs to a divine name, or whether two names meet at a theologically relevant point. The test measures numerical availability, not canonical significance.

\subsection{Why the Complete Declaration Still Comes First}

The full Ehyeh declaration was also tested by holding Asher fixed and varying the repeated outer expression. No attested $X$--Asher--$X$ control had the target's exact structural shape. In the larger synthetic comparison, 591 of 7,677 surface forms, 271 of 3,583 consonant families, and 53 of 786 distinct outer values produced a base-12 palindrome. Eighteen surface forms across ten families reproduced $393_{12}$, all because the outer expression had value 21.

This shows that palindrome completion is not arithmetically unique to the word Ehyeh. It also shows exactly what the synthetic test does and does not compare. It tests the formula $2x+501$ at other values of $x$; it does not produce another attested divine answer to Moses. For the argument of this paper, Ehyeh Asher Ehyeh is the primary object because it is the complete scriptural declaration. Ehyeh alone and the synthetic templates are mechanism checks that help explain the result without replacing it.

\subsection{What the Collapse Check Corrected}

The inherited language treated both 8 and 12 as stable collapse attractors. Varying the stopping rule showed an asymmetry:

\begin{itemize}
\item the same 10 primary rows reach 8 at stopping thresholds from 9 through 15;
\item 12 appears as a terminal value only when the rule is allowed to stop at 12 or above;
\item all eight relevant rows nevertheless equal 12 on the very first digit-sum step.
\end{itemize}

I therefore no longer call 12 a conventional attractor. I retain the exact first-step 12-sum pattern because that is what the numbers actually do. This is a good example of a correction making the paper more precise without making the observation disappear.

The scroll value requires a similar distinction. Its base-12 notation path is

\[
6556_{12}\rightarrow22_{10}\rightarrow4,
\]

while its converted decimal value follows

\[
11154_{10}\rightarrow12.
\]

The collapse to 4 remains meaningful within the four-letter interpretation of YHWH, but it is a separate path from the decimal-value sum of 12.

\subsection{What the Tests Cannot Decide}

The controls do not know that YHWH is YHWH or that Ehyeh Asher Ehyeh is the answer given in Exodus. They do not distinguish a sacred title from an ordinary phrase with the same number of letters or value. They do not test whether a scribe, translator, tradition, or providence placed a pattern intentionally. They also do not make nested names and related titles independent of one another.

What they can do is keep the numerical description honest. They show that palindromes are not rare in every base, that base 12 is not uniquely dominant in the frozen primary count, that the repdigit ladder is additively structured without being fully occupied, that the 8 layer is more rule-stable than the old 12-collapse language suggested, that Yeshua is the connective center of the tested network, and that the Christian title pattern deserves a prospectively frozen follow-up. They can rule out lexical or arithmetic uniqueness where controls reproduce a value. They cannot turn an equal number into an equal theological object.

The calculations remain on the page with their limits visible beside them. Appendix D supplies the complete protocol and statistics.
