\section{Conclusion: What Remains Open}

I began this paper with the sense that these names were doing more than producing isolated gematria values. After recalculation, source checking, expansion searches, and matched controls, I still think there is a pattern worth presenting. I would now describe it with more care and, in some places, with more wonder.

The strongest results are compact enough to see without specialized mathematics:

\begin{itemize}
\item YHWH becomes the base-12 palindrome $22_{12}$.
\item The source-secure two-digit nodes occupy rungs $\{1,2,3,4,5,7\}$ of the exact repdigit ladder $dd_{12}=13d$. Their six distinct-addend relations are maximal among six-rung subsets, while $66_{12}$ remains honestly unoccupied.
\item Shaddai becomes $222_{12}$ while retaining the decimal digits 314; its shared YHWH frame with Yeshua makes their exact decimal difference 72.
\item Ehyeh Asher Ehyeh becomes $393_{12}$, while its decimal digits sum to 12, its repeated outer occurrences contribute the subtotal 42 before Asher is added, and its visible frame is YHWH Echad at $33_{12}$.
\item Elohim becomes $72_{12}$ and separately gives the decimal palindrome 646 under Mispar Gadol.
\item El Roi and El Gibbor share the palindromic value 242, which reaches 8.
\item El Olam crosses decimal and base-12 palindrome layers under its two value systems.
\item Yeshua becomes $282_{12}$: terminal 8, exact sum 12, and a palindrome that places 8 inside the visible YHWH frame, echoing John 14:11.
\item Psalm 22 adds a localized textual convergence: \textit{Ayelet HaShachar} becomes $676_{12}$, whose displayed digits equal $26^2$ when read in decimal, while the opening lament contains \hebrew{ישוע} intact inside \hebrew{מישועתי}, ``from my salvation.''
\item Yeshua HaMashiach becomes $525_{12}$, with the article completing both the palindrome and the exact sum of 12 inside the $55_{12}$ Adonai frame.
\item Across all 132 repeated-frame palindromes, $282_{12}$ and $525_{12}$ are the only two whose center equals the decimal digital root and whose digits sum to 12.
\end{itemize}

At the canonical level, 22, 42, and 72 recur through different kinds of contact rather than one proven sequence. Psalm 119 also joins 22 and 8 in a textual structure: twenty-two alphabetic units of eight verses each. That correspondence does not identify decimal 22 with $22_{12}$, but it gives the visible relationship another canonical setting. The chapter total 929 converts exactly to $655_{12}$, and the only digit that can close it on the right as a palindrome is 6. The resulting $6556_{12}$ has outer digits summing to 12 and the complete $55_{12}$ value of Adonai at its center. Its notation collapses through decimal 22 to 4; its converted decimal value sums separately to 12. Among all 132 comparable one-digit closures, it alone combines the notation sum of 22 with the converted-value sum of 12. I no longer describe that object as though every step were one inevitable conversion. I still find the completed structure striking.

The audit also changed the paper in necessary ways. Some names had to be corrected. Some proposed titles were not titles in their cited verses. Some equalities disappeared when an article was restored. On an expression-row count, base 3 has the highest raw palindrome total in the repository-locked primary corpus. When exact numerical values are counted once, base 12 ties for first under both value systems. The matched controls do not make the primary base-12 count statistically decisive. The old language of a 12 attractor was too strong. Yeshua's value is not lexically unique, named outer frames occur in 23 of the 30 eligible value layers in the full expanded registry, the five anchors are not statistically privileged among all attainable alternatives, and the $X$--Asher--$X$ mechanism can produce other palindromes.

None of those corrections turns $22_{12}$ back into 26 on the page, removes the 8 from $282_{12}$, breaks $525_{12}$, creates a third solution in the complete 132-member family, or makes the complete Ehyeh formula behave like Ehyeh alone. Nor do the controls reproduce the identity and scriptural setting of the names whose arithmetic they imitate. They change the scale of the conclusions, not the existence of the calculations.

One robustness result deserves to be read from both directions. When Yeshua is removed, most of the network's cross-name connectivity disappears. As a statistical statement, the network depends heavily on one node. Within Christian theology, Yeshua standing at the connective center may be exactly what gives the architecture coherence. I do not think the numerical test can choose between those descriptions, and I do not want the paper to choose for the reader.

This is where I want the paper to stop telling the reader what to think. The numerical architecture may reflect features of Hebrew morphology, the way the corpus was selected, traditional development, deliberate arrangement, providential order, chance, or several of these at once. Mathematics can test some parts of that list more readily than others. It cannot collapse all of them into one final digit.

My own interest lies in the convergence. The repeated two-digit values form a single ladder whose occupied biblical rungs are unusually connected without being complete. Yeshua places 8 inside the visible YHWH signature 22, visually echoes the reciprocal indwelling language of John 14:11, sums to 12, becomes the connective center of the tested network, and yields a matched collision set partitioned through 12, 8, and 4. Psalm 22 adds another meeting point: a Psalm already placed at the crucifixion carries $676_{12}$ in its superscription, displays the decimal square of YHWH's value, and contains the consonants of Yeshua inside the language of salvation in its opening lament. Yeshua HaMashiach places its own decimal root inside the Adonai signature 55 and recalls the confession that Jesus Christ is Lord. Together the two Yeshua forms occupy the only two solutions in the complete repeated-frame family. Shaddai shares Yeshua's YHWH frame and stands exactly 72 away. A complete divine declaration acquires a form its repeated component does not possess and carries YHWH Echad as its frame. An added title moves 314 to 345, from a $\pi$ echo to a Pythagorean one. A canonical construction places Adonai at its center, passes through 22, and ends at 4. Each observation is modest in isolation. Together, they form the architecture explored here.

I offer that architecture as a finding, not a verdict. The appendices explain every step, and the repository preserves the complete rows. What the pattern finally means is left where I believe it belongs: with the reader.
