\section*{Sources and References}
\addcontentsline{toc}{section}{Sources and References}

The primary texts below support the manuscript's historical and textual conventions. Repository-generated tables, protocols, and control results are documented separately in the technical appendices.

\begin{thebibliography}{99}

\bibitem{oshb}
Open Scriptures.
\textit{MorphHB: Open Scriptures Hebrew Bible}.
Westminster Leningrad Codex with morphology.
Repository revision \texttt{3d15126fb1ef74867fc1434be1942e837932691f}.
\url{https://github.com/openscriptures/morphhb}.

\bibitem{sefaria_library}
Sefaria.
\textit{The Sefaria Library} and Search API.
Digital editions of Tanakh, rabbinic literature, and later Jewish texts.
\url{https://www.sefaria.org/texts}.

\bibitem{schechter1906gematria}
Schechter, Solomon, and Caspar Levias.
``Gema\d{t}ria.''
\textit{The Jewish Encyclopedia}, vol.~5, pp.~589--592, 1906.
\url{https://www.jewishencyclopedia.com/articles/6571-gematria}.

\bibitem{seferyetzirah22}
\textit{Sefer Yetzirah} 2:1--2.
``Twenty-Two Letters of Foundation.''
Sefaria digital edition.
\url{https://www.sefaria.org/Sefer_Yetzirah.2.2?lang=en}.

\bibitem{kiddushin42}
Babylonian Talmud, \textit{Kiddushin} 71a:13.
The forty-two-letter Name tradition.
William Davidson digital edition, Sefaria.
\url{https://www.sefaria.org/Kiddushin.71a.13?lang=bi}.

\bibitem{bahya72}
Rabbeinu Bahya ben Asher.
Commentary on Exodus 14:21.
The three 72-letter verses and the seventy-two triplets.
Sefaria digital edition.
\url{https://www.sefaria.org/Rabbeinu_Bahya%2C_Shemot.14.21.1?lang=bi}.

\bibitem{vitalexpansions}
Vital, Hayyim.
\textit{Sha'ar HaHakdamot}, Zeir Anpin and Nukba 18:1.
AB, SAG, MAH, and BEN expansion labels.
Sefaria digital edition.
\url{https://www.sefaria.org/Sha'ar_HaHakdamot%2C_Zeir_Anpin_and_Nukba.18.1?lang=bi}.

\bibitem{josephus22}
Josephus, Flavius.
\textit{Against Apion} 1.38--41.
Translated by William Whiston.
Perseus Digital Library, Tufts University.
\url{https://www.perseus.tufts.edu/hopper/text?doc=Perseus:text:1999.01.0216:book=1:section=38}.

\bibitem{bible_canon24}
``Bible Canon.''
\textit{The Jewish Encyclopedia}, 1906.
The twenty-two- and twenty-four-book enumerations.
\url{https://www.jewishencyclopedia.com/articles/3259-bible-canon}.

\bibitem{project929}
929: Tanakh Together.
``About 929.''
The 929-chapter reading cycle and its received chapter division.
\url{https://www.929.org.il/pages/aboutEN.html}.

\bibitem{verse_division}
``Verse-Division.''
\textit{The Jewish Encyclopedia}, 1906.
Chapter divisions in Hebrew printed editions.
\url{https://www.jewishencyclopedia.com/articles/14682-verse-division}.

\bibitem{biblica_mark}
Biblica.
\textit{Habrit Hakhadasha/Haderekh (The Way) Hebrew New Testament}, Mark 1.
\href{https://www.biblica.com/bible/hd/\%D7\%94\%D7\%91\%D7\%A9\%D7\%95\%D7\%A8\%D7\%94-\%D7\%A2\%D7\%9C-\%D7\%A4\%D7\%99-\%D7\%9E\%D7\%A8\%D7\%A7\%D7\%95\%D7\%A1/1/}{Biblica online text}.

\end{thebibliography}
